---
title: "INVAR2 Analysis"
output:
  html_document:
    dev: 'svg'
    df_print: 'tibble'
    toc: TRUE
    toc_float: TRUE
---

## Cohort by Mutant Context Plot

```{r fig.width = 6, fig.height = 5, echo = FALSE}
plots$P1
```

## AF by mutation class

```{r fig.width = 6, fig.height = 7, echo = FALSE}
plots$P2
```

## Mutations per patient captured and passing pipeline filters

```{r fig.width = 6, fig.height = 7, echo = FALSE}
plots$P3
```

## Mutation class distribution by cohort

```{r fig.width = 6, fig.height = 5, echo = FALSE}
plots$P4
```

## Case vs control error rates

```{r fig.width = 8, fig.height = 4, echo = FALSE}
plots$P5
```

# Summary Plots

## Background error rates

```{r fig.width = 8, fig.height = 4, echo = FALSE}
plots$P7
```

## Error rate comparison - both strands

```{r fig.width = 6, fig.height = 3, echo = FALSE}
plots$P9a
```

## Error rate comparison - locus noise

```{r fig.width = 6, fig.height = 3, echo = FALSE}
plots$P9b
```

## Error rate comparison - locus noise &amp; both strands

```{r fig.width = 6, fig.height = 3, echo = FALSE}
plots$P9c
```

## Filtering comparison

```{r fig.width = 6, fig.height = 4, echo = FALSE}
plots$P20
```

# Outlier suppression plots

## Data retained

```{r fig.width = 5, fig.height = 6, echo = FALSE}
plots$P6
```

## Background polishing

```{r fig.width = 15, fig.height = 12, echo = FALSE}
plots$P8
```

# Tumour AF in observed and unobserved loci.

```{r fig.width = 5, fig.height = 4, echo = FALSE}
plots$P10
```

# Fragment size per cohort

With different levels of error-suppression.

```{r fig.width = 6, fig.height = 5, echo = FALSE}
plots$P11
```

# Enrichment level

```{r fig.width = 6, fig.height = 5, echo = FALSE}
plots$P12
```

# Receiver Operating Characteristic (ROC) Plots

With size:

```{r fig.width = 4, fig.height = 3, echo = FALSE}
plots$P13a
```

Without size:

```{r fig.width = 4, fig.height = 3, echo = FALSE}
plots$P13b
```

# IR (depth) to IMAF

```{r fig.width = 6, fig.height = 4, echo = FALSE}
plots$P14
```

# Waterfall Plots

## Detectable vs non detectable using dPCR

```{r fig.width = 10, fig.height = 5, echo = FALSE}
plots$P15
```

## Cancer genomes

```{r fig.width = 10, fig.height = 5, echo = FALSE}
plots$P16
```

# dPCR comparison plot

```{r fig.width = 8, fig.height = 5, echo = FALSE}
plots$P17
```

# Mutation Tracking

```{r, echo = FALSE}
toYesNo <- function(v) { ifelse(v, 'Yes', 'No' ) }
mutationTrackingTable %>%
    mutate_if(is.logical, toYesNo) %>%
    kable()
```
